Results

### 2018-06-25 02_analysis.Rmd
Don't hardcode pdf + remove ..

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

@@

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](../output/figures/summary-table/", file_name, ".pdf)")

@@

  output <- data_frame(spark = md_img, summary = inline_summary)
}

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
```

>>>>

---
title: "Results"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args: [
      "--default-image-extension=png"
    ]
editor_options: 
  chunk_output_type: console
---

@@

  file_name <- gsub("\\.| ", "_", tolower(variable))
  md_img <- paste0("![](output/figures/summary-table/", file_name, ")")

@@

  output <- data_frame(spark = md_img, summary = inline_summary)
  return(output)
}

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(., where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
```
